---
title: "EDA on US Crime Data"
author: "Faisal Amir Maz"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cosmo
    highlight: tango
    toc: true
    toc_float:
      collapsed: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

link to the dataset: https://www.kaggle.com/datasets/jgiigii/uscrimesdataset


```{r}
# Libraries

library(dplyr)
library(lubridate)
```
# Wrangling

# Reading The Data
```{r}
#read the data
crime <- read.csv("Crime.csv")
head(crime)
```

```{r}
glimpse(crime)
```

```{r}
length(unique(crime$Crime.Name3))
table(crime$Crime.Name3)
```

## Summary on unique values on every column
Offence Code: having 342 unique values
CR Number has 200k unique
Nibrs Code has 58 unique values https://ucr.fbi.gov/nibrs/2011/resources/nibrs-offense-codes
67 cities
11 states (305k crime happened in State MD (Maryland))
8 agencies (MCPD has 200k  (montgomery county Police Departement))
99 places
16 sectors
57 Beats
807 PRA
33 street types
Crime.Name1 has 6 unique values
Crime.Name2 has 60 unique values
Crime.Name3 has 337 unique values

```{r}
sum(duplicated(crime))
```
No duplicated data


## Converting the data types
```{r}
crime <- crime %>% 
  mutate(State = as.factor(State)) %>% 
  mutate(Sector = as.factor(Sector)) %>% 
  mutate(NIBRS.Code = as.factor(NIBRS.Code)) %>% 
  mutate(Street.Type = as.factor(Street.Type)) %>% 
  mutate(Agency = as.factor(Agency)) %>% 
  mutate(Crime.Name1 = as.factor(Crime.Name1))
```


```{r}
crime$Dispatch.Date...Time <-  mdy_hms(crime$Dispatch.Date...Time)
crime$Start_Date_Time <-  mdy_hms(crime$Start_Date_Time)
crime$End_Date_Time <-  mdy_hms(crime$End_Date_Time)
tail(crime)

# abis ini select data tahunnya dari 2019 ke 2020 aja (buat liat perbedaan tahun setelah pandemi dansebelum pandemi)
# lebih spesifik (kalo 2 tahun masih berat pake 1 tahun aja yaitu 2020)

```


# Exploratory
```{r}
crime %>% 
  group_by(Crime.Name1) %>% 
  summarise(n())
```

```{r}
name1_other <- crime %>% 
  filter(Crime.Name1=="Other")

unique(name1_other$Crime.Name2)
```

```{r}

crime$year <- year(crime$Start_Date_Time)
crime$month <- month(crime$Start_Date_Time, label = T)
crime$day_of_week <- wday(crime$Start_Date_Time, label = T)
crime$hour <- hour(crime$Start_Date_Time)
```

```{r}
head(crime)
```


## Group By Year


```{r}
crime_year <- crime %>% 
  group_by(year) %>% 
  summarise(n())

crime_year
```

## Group by Month
```{r}
crime_month <- crime %>% 
  group_by(month) %>% 
  summarise(n())

crime_month
plot(crime$month)
```

## Group by Day of Week
```{r}
crime_dayofweek <- crime %>% 
  group_by(day_of_week) %>% 
  summarise(count = n())

crime_dayofweek
plot(crime$day_of_week)
```
## Further Groupping 
```{r}
crime %>% 
  group_by(hour) %>% 
  summarise(count = n()) %>% 
  arrange(-count)

```
```{r}
crime_place <- crime %>% 
  group_by(Place) %>% 
  summarise(count = n()) %>% 
  arrange(-count)

crime_place
```


```{r}
crime %>% 
  group_by(Crime.Name1) %>% 
  summarise(count = n())

plot(crime$Crime.Name1)
```
```{r}
sum(is.na(crime$Crime.Name1))
```
```{r}
crime %>% 
  group_by(City) %>% 
  summarise(count = n()) %>% 
  arrange(-count)
```
```{r}
sum(is.na(crime))
```

```{r}
nrow(crime)
```
```{r}
dn <- function(x){
  if(x > 6 & x < 18){x <- "day"}
  else{x <- "night"}
}
```

```{r}

```

```{r}
crime$day_night <- sapply(crime$hour, dn)
```

```{r}
head(crime)
```

```{r}
crime$day_night <- as.factor(crime$day_night)

```
```{r}
table(crime$day_night)
```

```{r}
crime$case_duration <- difftime(
  time1 = crime$End_Date_Time,
  time2 = crime$Start_Date_Time,
  units = "hours"
)


head(crime)
```

```{r}
duration_clean <- na.omit(crime$case_duration)

range(duration_clean)
```
# Visualization
```{r}
library(ggplot2)
library()
```

